\section{Contribution and AI-Use Record}

This appendix is included because the midterm requirement asks for a short contribution table and AI-use record in the report appendix. The team should complete the TODO rows before final submission.

\subsection{Contribution Record}

\begin{longtable}{|p{0.17\linewidth}|p{0.22\linewidth}|p{0.36\linewidth}|p{0.15\linewidth}|}
\hline
\textbf{Member} & \textbf{Module} & \textbf{Files / deliverables} & \textbf{Evidence} \\
\hline
TODO: Name & Data structure & TODO: list SQL, Python, CSV, Markdown, screenshots, or video evidence. & TODO \\
\hline
TODO: Name & Frontend & TODO: list frontend files, screenshots, video, or deployed prototype evidence. & TODO \\
\hline
TODO: Name & Image algorithm & \texttt{main.py}, \texttt{src/}, \texttt{config.yaml}, \texttt{setup.ps1}, \texttt{requirements.txt}, \texttt{README.md}, \texttt{tests/test\_core.py}, sample output evidence. & Unit tests, sample runs, GitHub commit \texttt{3a99c09}. \\
\hline
\end{longtable}

\subsection{AI-Use Record}

\begin{longtable}{|p{0.17\linewidth}|p{0.25\linewidth}|p{0.34\linewidth}|p{0.14\linewidth}|}
\hline
\textbf{Member / module} & \textbf{AI or tool assistance} & \textbf{Output adopted} & \textbf{Review} \\
\hline
Data structure & TODO & TODO & TODO \\
\hline
Frontend & TODO & TODO & TODO \\
\hline
Image algorithm & AI assistant for planning, coding support, documentation, and report drafting; Ultralytics YOLOv8n for object detection. & Implemented module structure, code organization, README, testing workflow, and report language were reviewed and adapted. & Reviewed through code inspection, tests, and sample outputs. \\
\hline
\end{longtable}

\subsection{Evidence Checklist Before Submission}

\begin{itemize}
  \item Add screenshots or video links showing frontend progress.
  \item Add database screenshots or command outputs showing schema creation and simulated data import.
  \item Add image algorithm screenshots showing CSV output, terminal test result, and at least one annotated detection result if available.
  \item Confirm repository access is granted to assessors.
  \item Confirm the repository excludes secrets, API keys, personal data, and confidential raw images.
\end{itemize}
