\section{Progress and Implemented Work}

This section compares the team's current progress against the expected midterm status: stable scope, agreed architecture, implemented baseline or core module, evidence of progress, identified risks, and clear ownership.

\moduleplaceholder{Data Structure Module Progress}{Describe the completed SQL schema, simulation data generator, CSV generation, import workflow, module interface documentation, and any test/import evidence. Add file names and screenshots if available.}

\moduleplaceholder{Frontend Module Progress}{Describe implemented pages/components, current UI state, mocked or real data connection, screenshots, and remaining frontend work. Add file names and screenshots if available.}

\subsection{Image Algorithm Module Progress}

The image algorithm module has been implemented as a CPU-based YOLOv8n baseline under the repository folder \texttt{image\_algorithm/} or the corresponding image algorithm folder in the shared project. Its purpose is to convert local images, or frames extracted from a future video stream, into structured seat status records.

The implemented module includes:

\begin{itemize}
  \item \texttt{main.py} as the command-line entry point;
  \item \texttt{src/detector.py} for YOLO model loading and inference;
  \item \texttt{src/geometry.py} for detection box and seat ROI matching;
  \item \texttt{src/state.py} for converting person/object signals into seat states;
  \item \texttt{src/storage.py} for Redis and MySQL integration;
  \item \texttt{src/pipeline.py} for the complete image-to-status workflow;
  \item \texttt{config.yaml}, \texttt{school\_test\_config.yaml}, and \texttt{web\_samples\_config.yaml} for reproducible configuration;
  \item \texttt{setup.ps1}, \texttt{requirements.txt}, and \texttt{README.md} for teammate setup;
  \item unit tests under \texttt{tests/}.
\end{itemize}

The module supports two modes. In normal mode, it reads \texttt{seat\_config} from MySQL, writes the latest seat states to Redis, and inserts historical rows into MySQL \texttt{seat\_status\_log}. In local demonstration mode, it can run with \texttt{--dry-run --skip-mysql --skip-redis}, use fallback seats from YAML, and generate \texttt{outputs/latest\_seat\_status.csv}. This allows the image logic to be tested even when local database services are not configured.

The current state rules are:

\begin{itemize}
  \item inactive seat: \texttt{unavailable};
  \item person detected in ROI: \texttt{occupied}, with \texttt{suspect\_duration = 0};
  \item no person but object detected: accumulate \texttt{suspect\_duration}; if it reaches the threshold, output \texttt{suspected};
  \item no person and no object: \texttt{free}, with \texttt{suspect\_duration = 0}.
\end{itemize}

The module was uploaded to the shared GitHub repository in commit \texttt{3a99c09} with the message \texttt{Add image algorithm module}. The upload intentionally excluded virtual environments, model weights, local password files, real school images, third-party sample images, and generated output files.
