\section{Plan to Final Delivery}

The remaining plan should convert the midterm baseline into an integrated final prototype. The plan below should be adjusted by the team after the data structure and frontend members add their current progress.

\begin{longtable}{|p{0.18\linewidth}|p{0.42\linewidth}|p{0.25\linewidth}|}
\hline
\textbf{Area} & \textbf{Remaining task} & \textbf{Owner / dependency} \\
\hline
Data structure & Finalize schema, generated data, import script, and backend-facing data format. & Data structure member; backend/frontend agreement. \\
\hline
Frontend & Complete UI screens, connect to backend/API or mock endpoint, and prepare screenshots/video evidence. & Frontend member; depends on API fields. \\
\hline
Image algorithm & Connect frame extraction from videos or camera source; calibrate ROI for real seats; run Redis/MySQL integration tests. & Image algorithm member; depends on camera/data availability. \\
\hline
Evaluation & Collect representative real library frames, label seat status, and evaluate false positives/false negatives. & Whole team; depends on data access. \\
\hline
Integration & Verify end-to-end flow from image output to database/cache to frontend display. & Whole team. \\
\hline
Final report/demo & Prepare final evidence, screenshots, video, and updated contribution/AI-use record. & Whole team. \\
\hline
\end{longtable}

For the image algorithm module, the most important final-delivery step is moving from local image folders to sampled video frames. The core algorithm does not need to change: a video stream can be sampled into frames, and each frame can be processed by the same YOLO + ROI + state-machine pipeline. This keeps the current implementation relevant for the final system.

\todobox{Teammates should replace the owner/dependency column with real names and dates. Add milestone dates if required by the supervisor.}
